---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Shinyapp of Access to Clean Fuels based on Population


## The shinyapp is created by Yin Shan Ho 31201474

This is a template that contains materials to create a shiny gadget application
for assessment 2. You will need the following packages installed to 
generate the gadget from this template:

```{r, eval = FALSE}
install.packages(c("shiny", "crosstalk", "plotly", "DT", "tidyverse", "here", "shinyWidgets"))
```

## How to run the app

This app is the proportion access to clean fuels and technologies for cooking based on population to GDP. The **color of the chart was chosen based on the Olympics Rings** which colors represent the five continents.  
The function of the chart are as follow:

 > Chart Tab
 
- **The chart can be shown in logged or linearized** form by switching the button titled'"Linear/Log Selector" at the top left-hand corner. 

- **Small countries which population below 1 million can be filtered** by the checkbox titled "Hide countries < 1 million population" at top right-hand corner.

- **The countries in the plot can be selected** by directly clicking the the points in the chart or inputting the country in the box titled "Select Countries to show in the Plot".  
**NOTE**: The selected data can be reset by double clicking the plot.

- **The time of the Data can be shown accordingly** to the setting of the sliderbar titled "Year" at the bottom.   
**NOTE**: The data can be shown by individual year or the range of the year by moving the slider bar.

> Table Tab

- **The countries in the table can be selected** by inputting the country in the box titled "Select Countries to show in the Table".

- **The time of the Data can be shown accordingly** to the setting of the sliderbar titled "Year" in the chart tab.  
**NOTE**: The data of the table can be shown by the selected beginning and the ending year or individual year specified.

The data of the app is downloaded from the [World Bank]( https://databank.worldbank.org/reports.aspx?dsid=2&series=EG.CFT.ACCS.ZS). Whereas the shinyapp was made based on the chart from [Our World in Data](https://ourworldindata.org/grapher/access-to-clean-fuels-for-cooking-vs-gdp-per-capita?time=earliest..2016). 

## Session Info

```{r session-info}
utils::sessionInfo()
```
